Hydras \& Co.

### 2022-02-26 doc/gaia-chapter.tex
improve redaction of gaia-chapter.tex

In case of name clash (for instance the type \texttt{T1} of ordinal terms below $\epsilon_0$), we often added a one-letter prefix to names : \texttt{g} or \texttt{G} for \gaia, \texttt{h} or \texttt{H}
for \HydrasLib.

@@

The \gaiaHydras entry point is the file
\href{../theories/html/gaia_hydras.T1Bridge.html}%
{\texttt{theories/gaia.T1Bridge.v}}, which requires modules both from \HydrasLib and \gaia. By default, we give priority to \gaia's notation and vocabulary.

\inputsnippets{T1Bridge/Requirements}

@@

\subsubsection{Renamings}

Most used constants and functions are also unambiguously renamed.

@@

\subsubsection{Translation functions and data refinement}

The bridge between both libraries is made of two functions.

\inputsnippets{T1Bridge/h2gG2hDef}

>>>>

The modules are located in {\texttt{theories/gaia/*.v}}.
The main entry point is
\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge}, which requires both Gaia's \texttt{ssete9} and a few modules of \texttt{theories/ordinals/Epsilon0}.

Other modules are dedicated to the adaptation of several notions of \HydrasLib to \mathcomp's and \gaia's vocabulary and structures.
By default, we give priority to \gaia's notation and vocabulary.

\subsection{The \texttt{T1Bridge} Module}

\texttt{T1Bridge} starts with a few requirements.
\inputsnippets{T1Bridge/Requirements}

Because of the common origin of \HydrasLib and \gaia, both libraries share the common name \texttt{T1} (data type of ordinal terms below $\epsilon_0$). As mentionned before, the bare name \texttt{T1} is given by priority to \gaia, and we prefix this name with an \texttt{h} (for ``hydras'') to refer to
\href{../theories/html/Epsilon0.T1.html}{hydras.Epsilon0.T1.T1}.

Many constants are common to \HydrasLib and \gaia. The following notations allow us to get rid of possible ambiguities, still
keeping with the prefix convention: ``h'' for \HydrasLib, ``g'' for \gaia.

\subsection{Translation functions and data refinement}

The bridge between both libraries is made of two straightforward bijections.

\inputsnippets{T1Bridge/h2gG2hDef}
\inputsnippets{HydraGaia_Examples/ExamplesG2H}

The function \texttt{g2h} is also used to provide a ``pretty'' printing of Cantor normal forms (through \texttt{Epsilon0.T1.pp}).

\inputsnippets{T1Bridge/T1ppDef}

\inputsnippets{HydraGaia_Examples/T1pp}

\section{Importing Material from \Hydras}

@@

@@

@@
